Optimal Fitting of Planar Curves to Prescribed Constraints

### 2013-07-18 idp/documentation/paper.tex
continued working on usability section

	\section{Usability of Curve Design Software}

		When trying to improve something, it seems advisable to take a step back and thoroughly research the causes of its shortcomings so as to find a way to improve it without making the same or similar mistakes. In the context of curve design tools, this can be achieved by analyzing and modelling the process that people use when designing curves. Once such a model has been obtained, it can be used to understand the issues with current tools as well as to propose criteria for good curve design tools.

		\subsection{Shortcomings of Existing Curve Design Software}

@@

		\subsection{Properties of Good Curve Design Software}

@@

			% moving from implementation detail to differential geometric specification
			% implementation section of https://code.google.com/p/kurve/wiki/Foundation

>>>>

		% TODO: make sure introduction does not overlap with start of next section regarding both content and wording

	\section{Usability of Curve Design Tools}

		When trying to improve something, it seems advisable to take a step back and thoroughly research the causes of its shortcomings so as to find a way to improve it without making the same or similar mistakes. In the context of curve design tools, this can be achieved by analyzing and modelling the process that people use when designing curves. Once such a model has been obtained, it can be used to understand the issues with current software as well as to propose criteria for good curve design tools.

			By observing the process that most people seem to go through when designing curves using vector graphics software, the following model appears plausible.

			\begin{enumerate}
				\item obtain the source curve as either a real or a mental image of the curve
				\item extract a set of properties from the source curve that uniquely identify it
				\item provide these properties to the software
				\item have the software turn them into the result curve
			\end{enumerate}

			Steps 2 to 3 are then repeated on portions of the curve in order to make small adjustments until the result curve is sufficiently similar to the source curve.

			Step 1 is of course independent of any software that may be used by the designer. Step 2 and 3 are strongly influenced by the choice of design tool, in that the software dictates which properties it accepts as descriptions for curves (the `language' the software uses). Finally, the success in step 4 depends solely on the ability of the software to turn descriptions of curves that are given to it into mathematical curves.

			The influence which the design tool has on the success or failure of this whole process thus depends on the following key points.

			\begin{itemize}
				\item Can the language describe curves succinctly and uniquely?
				\item Is it easy for humans to `read' the language from curves?
				\item Is it easy for humans to `speak' the language to the software?
				\item Is it possible for software to build curves from descriptions in the language?
			\end{itemize}

			At this point it seems obvious that the choice of language is the single most influential one when it comes to the usability of curve design software. Thus, usability analysis in the subsequent sections will focus almost exclusively on this concept of language and the key points made in the list above.

		\subsection{Shortcomings of Existing Curve Design Tools}

			Using the model of the curve design process established in the previous section, various tools available in current vector graphics software can be analyzed

			\subsubsection{Free-Hand Curves}

			\subsubsection{Bézier Splines}

			\subsubsection{Spiro Splines}

@@

		\subsection{Criteria for Good Cruve Design Tools}

@@

			% with language being this important, it seems irresponsible to simply choose to use the mathematical parameters of the model as the language
			% moving from implementation detail to differential geometric specification
			% implementation section of https://code.google.com/p/kurve/wiki/Foundation
